Convex Surrogates via Polyhedral Losses

### 2019-05-14 neurips-19/poly-embed.tex
Minor changes to notes on proofs.  Confused on where we can/can't use elicitation in proofs

We omit the details connecting this definition to consistency, and instead refer the reader to \raf{HARI \cite{ramaswamy2018consistent}} (See the proof of Theorems 8.1-8.3.).
\raf{We could flesh this out if we want.  Might be worth it.  Their entire proof(s) establish $\delta$-separation, and then the line ``The Theorem simply follows from linearity of expectation.''}

@@

\begin{proposition}\label{prop:embed-bayes-risks}
  A loss $L$ embeds discrete loss $\ell$ if and only if $\risk{L}=\risk{\ell}$.
  % A loss $L:\reals^d\to\reals^\Y$ embeds discrete $\ell:\R\to\reals^Y$ if and only if $\risk{L}=\risk{\ell}$.
\end{proposition}
\begin{proof}
  \raf{Use distributions on the interior of the cells; since the risk is differentiable there, the loss is uniquely defined, and thus the same, and the same throughout the cell.}
  \jessie{Alluded to in COLT Lemma 11 and Prop 12 (Lemma~\ref{lem:finite-full-dim} and Prop~\ref{prop:embed-trim} here), but I don't see us prove this in the original paper.}

@@

  \jessie{Not sure on this one, just FYI.  I think it's a corollary of COLT Prop 12, now Prop~\ref{prop:embed-trim}.}
  Now, to see that $\risk{\ell} = \risk{L} \implies L$ embesds $\ell$, consider $F$ to be the set of facets of the loss of $\risk{L}$.
  For each facet $f \in \F$, we know by nonredundancy that there is some $p \in \inter{f}$ so that $\risk{L}$ is differentiable at $p$.
  Moreover, by Frongillo and Kash~\jessie{CITE... 2014 paper? Theorem 24?} we know that both $\ell$ and $L$ have a unique minimizer at $p$, and since the subgradients of the risks are the same (by their equality), we know the minimizers of the losses are also the same.
  Therefore, we can see (with more elaboriating) that $L$ embeds $\ell$.

@@

  For the reverse implication, suppose $\risk{L}$ is polyhedral. 
  For each facet $f \in F$ of $\risk{L}$, consider the report $u_f = \arginf_{u'} L(u', p)$ for some $p \in \inter f$.
  (Note that this $u$ will be unique regardless of the choice of $p\in \inter f$, since $\risk{L}$ is differentiable here.)
  Since $\risk{L}$ has a finite set of facets, the set $\R = \{u_f\}_{f \in F}$ \jessie{add that $F$ is full set of facets} is finite.
  Now define the discrete loss $\ell:\R \to \Y$ by $\ell(r,y) = L(r,y)$.

>>>>

We omit the details connecting this definition to consistency, and instead refer the reader to Ramaswamy et al.~\cite{ramaswamy2018consistent}. 
(See the proof of Theorems 8.1-8.3.).
\raf{We could flesh this out if we want.  Might be worth it.  Their entire proof(s) establish $\delta$-separation, and then the line ``The Theorem simply follows from linearity of expectation.''}

@@

\begin{proposition}\label{prop:embed-bayes-risks}
  A loss $L$ embeds discrete loss $\ell$ if and only if $\risk{L}=\risk{\ell}$.
  % A loss $L:\reals^d\to\reals^\Y$ embeds discrete $\ell:\R\to\reals^Y$ if and only if $\risk{L}=\risk{\ell}$.
\end{proposition}
\begin{proof}
  \raf{Use distributions on the interior of the cells; since the risk is differentiable there, the loss is uniquely defined, and thus the same, and the same throughout the cell.}
  \jessie{Stated in COLT Lemma 11 and Prop 12 (Lemma~\ref{lem:finite-full-dim} and Prop~\ref{prop:embed-trim} here), but I don't see us prove this in the original paper.}

@@

  \jessie{Not sure on this one, just FYI.  I think it's a corollary of COLT Prop 12, now Prop~\ref{prop:embed-trim}.}
  Now, to see that $\risk{\ell} = \risk{L} \implies L$ embeds $\ell$, consider $F$ to be the set of facets of the surface of $\risk{L}$.
  For each facet $f \in \F$, we know by nonredundancy that there is some $p \in \inter{f}$ so that $\risk{L}$ is differentiable at $p$.
  Moreover, by Frongillo and Kash~\cite[Theorem 2?]{frongillo2014general} \jessie{Check ref} we know that both $\ell$ and $L$ have a unique minimizer at $p$, and since the subgradients of the risks are the same (by their equality), we know the minimizers of the losses are also the same, up to relabeling the reports via a bijection.
  Therefore, we can see that $L$ embeds $\ell$, as $L(\varphi(r),y) = \ell(r,y)$ for all $r\in\R$ and $y \in \Y$.

@@

  For the reverse implication, suppose $\risk{L}$ is polyhedral. 
  For each facet $f \in F$ of $\risk{L}$, consider the report $u_f = \arginf_{u'} L(u', p)$ for some $p \in \inter f$.
  (Note that this $u$ will be unique regardless of the choice of $p\in \inter f$, since $\risk{L}$ is differentiable here.)
  Since $\risk{L}$ has a finite set of facets, the set $\R = \{u_f\}_{f \in F}$ is finite.
  Now define the discrete loss $\ell:\R \to \Y$ by $\ell(r,y) = L(r,y)$.
